---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `PakPMICS2018`: Multiple Indicator Cluster Survey (MICS) 2017-18 Data for Punjab, Pakistan

```{r,echo = FALSE, message = FALSE}
devtools::load_all(".")
```

###### Version : [`r getNamespaceVersion("PakPMICS2018")`](https://myaseen208.com/PakPMICS2018/); Copyright (C) 2019-2020: [UAF](https://web.uaf.edu.pk/); License: [GPL-2|GPL-3](https://www.r-project.org/Licenses/)


##### *Muhammad Yaseen*

Department of Mathematics and Statistics, University of Agriculture Faisalabad, Pakistan.

***

[![minimal R version](https://img.shields.io/badge/R>%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/PakPMICS2018)](https://cran.r-project.org/package=PakPMICS2018)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/PakPMICS2018?color=green)](https://CRAN.R-project.org/package=PakPMICS2018)
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/myaseen208/PakPMICS2018) -->

```{r, results='asis', echo=FALSE}
dver <- ifelse(test = gsub("(.\\.)(\\d+)(\\..)", "", getNamespaceVersion("PakPMICS2018")) != "",
               yes = getNamespaceVersion("PakPMICS2018"),
               no = gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/PakPMICS2018", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/PakPMICS2018", "/master/DESCRIPTION")))]))
cat(paste("[![develVersion](https://img.shields.io/badge/devel%20version-", dver, "-orange.svg)](https://github.com/myaseen208/PakPMICS2018)", sep = ""))
```

<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/myaseen208/PakPMICS2018/total.svg)] -->
[![Project Status: WIP](http://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/myaseen208/PakPMICS2018)

***

## Description
`r gsub("(<doi:)(.+)(>)", "[doi:\\2](https://doi.org/\\2)", gsub("\\n", " ", packageDescription("PakPMICS2018", fields = "Description")))`

## Installation
The package can be installed from CRAN as follows:

```{r, eval=FALSE}
install.packages("PakPMICS2018", dependencies = TRUE)
```



The development version can be installed from github as follows:

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("myaseen208/PakPMICS2018")
```


## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package = "PakPMICS2018")
```

## Links

[CRAN page](https://cran.r-project.org/package=PakPMICS2018)

[Github page](https://github.com/myaseen208/PakPMICS2018)

[Documentation website](https://myaseen208.com/PakPMICS2018/)



## Citing `PakPMICS2018`
To cite the methods in the package use:

```{r, eval = FALSE}
citation("PakPMICS2018")
```

```{r, echo = FALSE}
detach("package:PakPMICS2018", unload=TRUE)
suppressPackageStartupMessages(library(PakPMICS2018))
cit <- citation("PakPMICS2018")
# yr <- format(Sys.Date(), "%Y")
# cit[1]$year <- yr
# oc <- class(cit)
# 
# cit <- unclass(cit)
# attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
#                                      paste("\\(", yr, "\\)", sep = ""),
#                                      attr(cit[[1]],"textVersion"))
# class(cit) <- oc
cit
